The Feasibility of Stylometry as a Service

### 2013-12-12 paper/paper.tex
one last look.

A privacy enhancing technology that is designed to exist as a web
service faces different challenges than an application.  Attack
vectors open up on the service from active denial-of-service attacks
to passive sniffing.  A privacy web service must take great care to
ensure that service does not compromise its user's privacy.  In
Section \ref{sec:design} we provide our architecture and analysis the
security and privacy.

\section{Design}

@@

The architecture of Anonymouth is that of a conventional desktop
application.  It uses a layered architecture with essentially two main
components: the frontend Graphical User Interface (GUI) and the
backend, consisting of the Weka machine learning toolkit and Jstylo.
Jystlo is PSAL's stylometric analysis software.   Since Anonymouth was
designed as a monolithic application, there are direct dependencies
between the layers without the use of an adaptation layer.  Figure
\ref{fig:jsan} illustrates the architecture in a layered drawing.  In
this drawing, components, represented as boxes, can call software
below and to the right.

This design is sufficient for Anonymouth in its current form.  As a
desktop appliccation, the user can anonymize her and the document
locally without any additional attack vectors.

@@

\subsection{Requirements for Web Service}

The architecture for a web service imposes different requirements on
an application.  First and foremost, since Anonymouth is a privacy
enhancing technology, the web service \emph{must} not degrade the
privacy protection of the application.  This is a challenge when
migrating from a desktop to web service since the desktop application
does not use any networked communicaiton.  However, there is little
benefit to using Anonymouth on the web if it compromises one's
privacy.

\subsubsection{Low-latency.}
The web service as implemented is near-real-time, i.e. low-latency,
bounded primarily be the performance of Anonymouth. One key feature of
the current implementation is the asynchronous processing of
stylometric information, which allows a user to continually modify a
text while anonymity information is calculated in the background. The
latency of the response times for each stylometric analysis is on the
order of 1 to 2 minutes in the default configuration (see Performance
section for futher details).

A high latency system would not be well suited for a web service.  An
example high latency system could simply entail sending an encrypted
email to a third party who uses Anonymouth locally and returns the
encrypted result.  While this high-latency system seems trivial, note
that a naive implementation will reduce the user's privacy.  For
example, email is very subject to traffic analysis
\cite{Mathewson04practicaltraffic} and encrypted email is easy to
detect, therefore this act alone would raise suspiction.  If
this third party was offering a high-latency anonymiziation service
for numerous people, the network graph would be easy to detect.

@@

Availability is the measure of the measure of the accesibility and
realibility of the system, e.g. how well does it handle errors.
Interoperability refers to the degree with which a system can interact
with its components or other systems.  Modifiability is important for
large systems so that they can be easily maintained and scale.  The
response of the system to input is its performance.  Security is the
review of a system's ability to protect sensitive data and prevent
unautorized and undesired behaviour.  Testability is an important
factor not only in development but also in a deployed system to ensure
that the system is working as designed.  Usability is notoriously bad
for security software \cite{Whitten:1999:WJC:1251421.1251435} and
refers to the interaction design.  Lastly, by privacy we mean how well
a user's anonymitity is protected.

@@

There are many implemenation details to achieve availability that are
beyond the scope of this paper.  We attest that a stylometric service
needs to be available and should consider the effects of sudden
traffic increases.

@@

The stylometric web service we implemented is interoperable with the modern
web architecture.  Specifically, it should be a service based on
Representational State Transfer (REST)\cite{Fielding2000}.  REST web
services define a framework that is client-server, has a uniform
interface based on HTTP verbs, and supports a layered architecture.
These features are in-line with the goals of a stylometric web
service.  Using a REST service, the client software can be a web
browser, which is nearly ubiqiteious on mobile devices.

@@

One of the goals of the service is provide a platform for stylometric
research.  In this sense in must be modifable to accomodate different
kinds of experiments including ones not currently anticipated.
Software engineering best pratices are applicable here mainly having
well abstracted interfaces and modular components.  As a RESTful web
service, each endpoint should have a concise application programming
interface (API) for a given feature set.  For example, there should be
a stylometry endpoint that can process text and return features.
Other services, such as an adversarial stylometry service, should use
the stylometric service via its REST API.

@@

@@

{\bf Confidentiality.} The service must protect the confidentiality of
the user's data.  The user is trusting the service with their corpus
and document to anonymize and that must be revealed to unauthroized
users.  However, one of the goals of this service is to allow multiple
authors to collaborate.  In this case, the confidentiality
requirements are more interesting.  We don't specifiy an
implementation, but there are various techniques that could satisfy
this requirement.

@@

@@

@@

\begin{figure*}
  \centering
    \includegraphics[width=0.6\textwidth]{img/jsanaas.pdf}
  \caption{Example JSANaaS Architecture as a Deployment Diagram}
  \label{fig:jsanaas}
\end{figure*}
\section{Security Analysis}

@@

Although web accessbility may be a significant risk from a usability
standpoint, the anecdotal infrequency with which adversarial
stylometry software is used even among privacy-conscious users as
determined by conversations with colleagues of the authors
suggests that delivery of this functionality via a web page (or even
potentially via a browser plugin functional across multiple web pages)
may be an appropriate trade-off to make.

@@

{\bf Man in the middle attacks}: If a user accepts a rogue SSL
certificate, it may be possible to create a "man in the middle" attack
where the user believes she is communicating with a specific
Stylometry Service, but is infact communicating via an impersonated
target.

{\bf Replay attacks}: An evesdropper may replay a message to the
webservice in an attempt to surrepituously revert parts of the text to
earlier versions. This may be possible as it is not documented whether
the current implementation uses nonces when transmitting messages.

{\bf HTML5 Canvas attacks}: The etherpad implementation uses the new
'canvas' element introduced in HTML5 extensively. Recently an attack
has been documented \cite{BrowserTiming} whereby Firefox optimizations
in the implementation of the requestAnimationFrame method have been
used by to detect differences in link coloring across frames (allowing
an adversary to determine if a particular styometry service has been
visited, for instance).

Note: We do not know if any of these vectors allows for a specific
attack, but suggest they should be considered for any future
implementation research in the area of stylometric web services using
a similar architecture.

\section{Privacy and Anonymity Analysis}

The privacy of a user accessing the web service is expected to be
ensured via the use of TLS/SSL encryption for all data transmitted
between the client and server. The anonymity of the user is expected
to be promoted via the use of an Onion Routing protocol such as Tor,
to ensure that the IP of the client cannot be directly linked to the
IP of the service.

\section{Implementation Details}

We implemented a web application based on the Play Web Application
Framework in Java. This web application had a reference to a modified
version of JSAN which was forked from the PSAL Anonymouth repository
\cite{PSAL:github}. In addition the application has major dependencies
on JQuery, Twitter Bootstrap (for page layout), and Etherpad (an
open-source collaborative text editing web application and library)
\cite{etherpad}. Etherpad (specifically Etherpad Lite is the version
used here) in turn has major dependencies on node.js for building and
running the backend service.

At a high level the implementation is as follows: A user browses to
the Stylometry Service via a web browser. This causes the Play
Framework web application to serve up a web page with an Etherpad
control and instructions for the user to enter in the document they
wish to anonymize. The etherpad control is implemented as an iframe
which serves an Etherpad that is connected to the node.js server
running the Etherpad backend (both servers should reside on the same
domain, running on different ports). The page served by Play also
contains a button which allows the author to specify when he or she
would like to submit the document for anonymization to
Anonymouth. Because the Anonymouth analysis process depends on a
number of computationally-intensive algorithms (among them running SMO
analysis in Weka as well as a Basic-9 feature stylometric analysis) we
implemented this calculation asynchronously. When a user clicks the
button to run an analysis, JQuery is used to issue a HTTP POST
containing in the message body a JSON-encoded representation of the
current Etherpad text to an endpoint at
\url{/getAnonymouthInfoJSON}. During the time that the Anonymouth
analysis is underway, a spinner control from the spin.js library is
used to indicate to the user than an analysis is underway. The fact
that the request is made to Anonymouth asynchronously allows a user to
continue editing the text while an analysis is running, allowing for a
smooth user experience.

The web service as implemented currently supports only 1 author as the
assumption is made that the author has pre-configured the "doc set"
(also referred to as 'problem set' in Anonymouth source) that provides
references as to the author's own writing style, as well as writing
samples for other authors that will be used as a reference for writing
styles that are different than that of the active author. The user can
additionally configure the anonymouth properties file
(\texttt{anonymouthprop.prop}) in the jsan resources directory to influence
settings such as the feature set to use for stylometric identification
as well as the number of threads to use and maximum number of features
to analyze.

One configured, the call to the \texttt{getAnonymouthInfoJSON} input
will overwrite the "test.txt" file on disk that is configured in the
provided problem set. This will ensure that changing the document in
Etherpad forces an update to the test file and thus ensuring that the
'latest' document is always anonymized. Once the problem set has been
updated, the 'Anonymouth library' is invoked. The 'Anonymouth library'
is a forked version of the current Anonymouth application, which is
designed to be used behind a Swing/AWT rich client GUI. A number of
implementation challenges were present when trying to separate the
core anonymization logic of Anonymouth from its GUI implementation -
most specifically, although an 'engine' namespace exists which holds
much of the anonymization logic, significant dependencies still
existed between the 'engine' and the 'GUI' namespaces, specifically in
the event handlers associated with the Editor screen and the
\texttt{GUIMain} classes. Much of the work in this project consisted
of reducing the coupling between these two namespaces.

As much of the configuration logic was handled at the GUI layer (via
\texttt{ThePresident} and \texttt{GUIMain} classes) we took the
approach of refactoring the GUI layer to work in a 'headless' mode,
that is, without any windows launching. Long-term it would be
preferable to have no dependencies on the GUI namespace at all for the
Stylometry Service, however this could not be achieved in the
available timeframe for this project. The web service thus invokes a
modified version of the \texttt{ThePresident} class, which coordinates
reading configuration files, loading the configured problem set, and
using numerous libraries (JGAAP and Weka among them) to conduct an
adversarial stylometric analysis. The results are returned by the web
service in the form of a JSON-encoded list of words to remove, as well
as an indication of 'changes needed' to the current text to reach an
acceptable level of anonynmity.

@@

\section{Comparison to Stand-alone Application}

The stand-alone application has both advantages and disadvantages
relative to the web service. To start with advantages: it contains
more robust error handling, offers a GUI to create a problem set, and
provides a richer editing experience for anonymized
texts. Disadvantages concern ease of use (users must download and
execute a JAR file) and supported platforms (it is unlikely that this
JAR file will be supported on many mobile phones, for instance). The
Stylometry Service, in contrast, is potentially more accessible than
the standalone application: it can be accessed via mobile phones and
tablets, for instance. Likewise application delivery may be simpler -
nothing must be downloaded locally. Furthermore, the web application
maintains a 'timeline' of changes made to a text and also allows for
simple multi-party anonymization of documents.

Disadvantages to the web application include the fact that it offers
fewer anonymization features (for instance, highlighting of specific
text passages), instead focusing primarily on 'words to
remove'. Furthermore, its security footprint is less well known, as it
introduces a number of new dependencies / potential attack vectors
such as JQuery, Twitter Bootstrap, Etherpad Lite, node.js, etc.

\section{Deployment}

@@

\section{Single User Evaluation}

@@

\section{Multiple Concurrent User Evaluation}

TODO

\section{Evaluation of Architecture Qualities}

\subsection{Performance.}

The performance of the Stylometry Service as implemented is largely
determined by that of the Anonymouth service that it uses to get
stylometry suggestions. For an analysis of 1 500-word test document vs
23 documents from 4 'other' authors and using 8 training documents
from the to-anonymize author, we recorded a total of 67 seconds
required for the Anonymouth analysis, with less than 1 additional
second used to update the client UI, on a 3.3 Ghz Core i5 Ubuntu 12.04
Desktop machine, using 1 calculation thread for Anonymouth. These
results suggests that any attempts at performance optimization should
center around optimizing the performance of the Anonymouth
configuration.

After each stylometric analysis is complete, the web service ensures
all relevant anonymouth resources are closed. This allows the web
service to be used over a long period of time (20 or more
anonymization attempts have been tested) without memory leaks noted.

@@

\subsection{Testability.}

@@

@@

There are two significant contributions as a result of this work.  The
first is a stylometric web service.  This advances the usability
and capabilities of JSAN and provide a framework for more expansive
user testing in the future. The user testing results suggest that a
web interface may offer usability advantages while still providing a
meaningful increase in author anonymity.  The second contribution is that this is
the first framework for multi-author adversarial stylometry.  Our
results here suggest TODO.

@@

\begin{table}
  \centering
  \begin{tabular}{l | c}
    Milestone & Date\\
    \hline

    Document initial design & October 28\\
    Finish porting JSAN to a web service & November 4\\
    Add the Firebase editro & November 11\\
    Add the third party feature & November 18\\
    Conduct evaluation & November 25\\
    Provide Paper and Presentation & December 2

  \end{tabular}
  \caption{Project Milestones}
  \label{tab:milestones}
\end{table}

@@

The scope of this project is designed to completed in one Drexel
quarter, however we have several ideas for continued work.  With a web
service, we can offer real-time adversarial stylometry.  Assume Alice,
who has a blog, wants to anonymize her next blog post.  She would
connect to our web service, submit the URL for her blog and then write
her next post with adversarial stylometry.  This real-time data
crawling at this scale is simply not feasible with stand alone
software.

Now that a third party will be re-writing documents, we feel that it
is important to obfuscate the content from the re-writer.  One idea,
is to mix the document, perhaps with other documents, prior to
re-writing.  The re-writer would be presented with an otherwise
nonsensical document and would focus on re-write each sentence in her
native style.  The combined document, would contain $n$ author styles,
where $n$ is the number of re-writing authors.

>>>>

A privacy enhancing technology that is designed to exist as a web
service faces different challenges than an application.  Attack
vectors open up on the service from active denial-of-service attacks
to passive sniffing.  A privacy web service must take great care to
ensure that service does not compromise its user's privacy.

\subsection{Novelty}

Our novel contribution is the proposal of a stylometric web service
and identifying the features of such a service.  We have provided a
prototype implementation and identified areas of additional
improvement.  Lastly, we suggest combining research from Game
Artificial Intelligence to improve the usability and effectiveness of
stylometric techniques.

\subsection{Outline}
In Section \ref{sec:design} we provide our architecture and analysis the
security and privacy.  We provide several architectural and security
features that a stylometric web service must and should have.  Section
\ref{sec:security} provides a security analysis of the system design.
A privacy analysis is provided in Section \ref{sec:privacy}.  The
current state of the implementation is discussed in Section
\ref{sec:impl} which includes details on how to reproduce our
results.  Evaluation of the implementation and current architecture is
provided in Section \ref{sec:evaluation}.

\section{Design}\label{sec:design}

@@

The architecture of the current adversarial stylometric software,
Anonymouth, is that of a conventional desktop application.  It uses a
layered architecture with essentially two main components: the
frontend Graphical User Interface (GUI) and the backend, consisting of
the Weka machine learning toolkit and JStylo.  JStylo is PSAL's
stylometric analysis software.  Since Anonymouth was designed as a
monolithic application, there are direct dependencies between the
layers without the use of an adaptation layer.  Figure \ref{fig:jsan}
illustrates the architecture in a layered drawing.  In this drawing,
components, represented as boxes, can call software below and to the
right.

This design is sufficient for Anonymouth in its current form.  As a
desktop application, the user can anonymize her and the document
locally without any additional attack vectors.

@@

\subsection{Requirements for Web Service}\label{sec:reqs}

The architecture for a web service imposes different requirements on
an application.  First and foremost, since Anonymouth is a privacy
enhancing technology, the web service \emph{must} not degrade the
privacy protection of the application.  This is a challenge when
migrating from a desktop to web service since the desktop application
does not use any networked communication.  However, there is little
benefit to using Anonymouth on the web if it compromises one's
privacy.

@@

Availability is the measure of the measure of the accessibility and
reliability of the system, e.g. how well does it handle errors.
Interoperability refers to the degree with which a system can interact
with its components or other systems.  Modifiability is important for
large systems so that they can be easily maintained and scale.  The
response of the system to input is its performance.  Security is the
review of a system's ability to protect sensitive data and prevent
unauthorized and undesired behavior.  Testability is an important
factor not only in development but also in a deployed system to ensure
that the system is working as designed.  Usability is notoriously bad
for security software \cite{Whitten:1999:WJC:1251421.1251435} and
refers to the interaction design.  Lastly, by privacy we mean how well
a user's anonymity is protected.

@@

There are many implementation details to achieve availability that are
beyond the scope of this paper.  We attest that a stylometric service
needs to be available and should consider the effects of sudden
traffic increases.

@@

The stylometric web service we implemented is interoperable with the modern
web architecture.  Specifically, it should be a service based on
Representational State Transfer (REST) \cite{Fielding2000}.  REST web
services define a framework that is client-server, has a uniform
interface based on HTTP verbs, and supports a layered architecture.
These features are in-line with the goals of a stylometric web
service.  Using a REST service, the client software can be a web
browser, which is nearly ubiquitous on mobile devices.

@@

One of the goals of the service is provide a platform for stylometric
research.  In this sense in must be modifiable to accommodate different
kinds of experiments including ones not currently anticipated.
Software engineering best practices are applicable here mainly having
well abstracted interfaces and modular components.  As a RESTful web
service, each endpoint should have a concise application programming
interface (API) for a given feature set.  For example, there should be
a stylometry endpoint that can process text and return features.
Other services, such as an adversarial stylometry service, should use
the stylometric service via its REST API.

@@

However, we do specify that the service should be low-latency.  The
web service as implemented is near-real-time, i.e. low-latency,
bounded primarily be the performance of Anonymouth. One key feature of
the current implementation is the asynchronous processing of
stylometric information, which allows a user to continually modify a
text while anonymity information is calculated in the background. The
latency of the response times for each stylometric analysis is on the
order of 1 to 2 minutes in the default configuration.

A high latency system would not be well suited for a web service.  An
example high latency system could simply entail sending an encrypted
email to a third party who uses Anonymouth locally and returns the
encrypted result.  While this high-latency system seems trivial, note
that a naive implementation will reduce the user's privacy.  For
example, email is very subject to traffic analysis
\cite{Mathewson04practicaltraffic} and encrypted email is easy to
detect, therefore this act alone would raise suspicion.  If
this third party was offering a high-latency anonymization service
for numerous people, the network graph would be easy to detect.

@@

{\bf Confidentiality.} The service must protect the confidentiality of
the user's data.  The user is trusting the service with their corpus
and document to anonymize and that must be revealed to unauthorized
users.  However, one of the goals of this service is to allow multiple
authors to collaborate.  In this case, the confidentiality
requirements are more interesting.  We do not specify an
implementation, but there are various techniques that could satisfy
this requirement.

@@

Usability is often sacrificed for security in privacy and security
software.  Of course, the most secure system is the one that does not
communicate with any other entity.  The target audience for
stylometric software are authors, of varying technical capacity.
Recently, organizations like the Freedom of the Press Foundation
\cite{pressfreedom} have shown increasing interest in educating
journalists on cryptographic and privacy enhancing software.  While
usability is difficult to quantify, the service must be usable by
non-technical end users without a detailed knowledge in stylometry.

@@

The service must protect the privacy of its users.  Specifically, it
must not leak the corpus nor the target document.  It also must be
vulnerable to traffic analysis, as that could possibly lead to linkage
attacks.  Especially because the documents could contain references to
other accounts or activity that would make them prime for attacks as
discussed in \cite{Narayanan:2008:RDL:1397759.1398064}.

The privacy of the service should also be maintained.  A critical
difference between a web service and a standalone application is that
the software on a web service runs on third-party hardware.  While
perhaps obvious, this as fundamental trust issues.  Therefore, the
knowledge that a stylometric service is running in a certain
geographical area, or more specifically, on a specific Internet
Service Provider, could make it vulnerable to attacks.

Furthermore, it is assumed that the host of the service is trusted.
This is a significant assumption since users of most ``Cloud''
providers rent time on the hardware.  Worse, they are not the sole
users of said hardware and their application is shared with other
users.  The choice of a service provider is outside the scope of this
document, but this consideration should not be made lightly when
choosing where to deploy the service.

The service must not engage in browser fingerprinting
\cite{Eckersley:2010:UYW:1881151.1881152}.  If deployed behind a Tor
Hidden service, browsers should be nearly indistinguishable when
everybody is using the Tor Browser Bundle.  Debug information must be
kept to a minimum as well.  This service must use the ``Privacy by
Architecture'' approach \cite{Spiekermann_Cranor:2009} and ensure that
debug information and collection is kept to a minimum.  Debug
information is particularly sensitive since to re-create a bug, one
may need the target document.  However, under no circumstances should
the user's document be released to developers as that would compromise
the confidentiality of the document.  Plus, this extends opportunities
for attack vectors through debug channels.

@@

Figure \ref{fig:jsanaas} illustrates an example architecture with
qualities from Section \ref{sec:reqs}.  The main entry point is a
lightweight dispatcher that sits behind a Tor Hidden Service.  The
user only need to know this address and can connect to the service
through Tor.

The backend has several modular endpoints.  The first of which is a
directory service.  The directory service accepts registration from
other services and provides the location of the service when
queried.  This feature help to provide availability and testability.
Especially as a research platform, additional services or endpoints
may need to be added to the system.  A registration service tracks the
dynamic installation of such services and when all services in the
system check with the registration service, they can quickly use the
new addition.

\begin{figure*}
  \centering
    \includegraphics[width=0.6\textwidth]{img/jsanaas.pdf}
  \caption{Example JSANaaS Architecture as a Deployment Diagram}
  \label{fig:jsanaas}
\end{figure*}

Notice that each feature is split into its endpoint.  This also helps
with the modularity and availability.  Backup endpoints can be
registered with the registration service and all endpoints frequently
queried, or they can provide notifications, such that services
maintain their uptime.  This modularity also helps with moving the
location of the service.  As long as the lightweight front-end remains
known, all backend services can move without the knowledge of the
user.  Perhaps each individual backend service would be its own Tor
Hidden Service.  The onion addresses would only to be known to the
Registration Service.  However, as each Hidden Service connection is
six hops through Tor, the performance impact would have to be more
closely studied.

\section{Security Analysis}\label{sec:security}

@@

Although web accessibility may be a significant risk from a usability
standpoint, the anecdotal infrequency with which adversarial
stylometry software is used even among privacy-conscious users as
determined by conversations with colleagues of the authors
suggests that delivery of this functionality via a web page (or even
potentially via a browser plugin functional across multiple web pages)
may be an appropriate trade-off to make.

@@

{\bf Man in the middle attacks}: If a user accepts a rogue SSL
certificate, it may be possible to create a "man in the middle" attack
where the user believes she is communicating with a specific
Stylometry Service, but is in fact communicating via an impersonated
target.

{\bf Replay attacks}: An eavesdropper may replay a message to the
web service in an attempt to surreptitiously revert parts of the text to
earlier versions. This may be possible as it is not documented whether
the current implementation uses nonces when transmitting messages.

{\bf HTML5 Canvas attacks}: The etherpad implementation uses the new
'canvas' element introduced in HTML5 extensively. Recently an attack
has been documented \cite{BrowserTiming} whereby Firefox optimizations
in the implementation of the requestAnimationFrame method have been
used by to detect differences in link coloring across frames (allowing
an adversary to determine if a particular stylometry service has been
visited, for instance).

We do not know if any of these vectors allows for a specific
attack, but suggest they should be considered for any future
implementation research in the area of stylometric web services using
a similar architecture.

Lastly, this application uses numerous third party libraries and
technologies.  The added complexity from each additional library or
toolkit, exposes the service to additional vulnerabilities.  It also
makes the software more difficult to audit by third parties.
Deploying a Stylometric service required numerous frameworks, some of
which are in very rapid development.

\section{Privacy and Anonymity Analysis}\label{sec:privacy}

The privacy of a user accessing the web service is expected to be
ensured via the use of TLS/SSL encryption for all data transmitted
between the client and server. The anonymity of the user is expected
to be promoted via the use of an Onion Routing protocol such as Tor,
to ensure that the IP of the client cannot be directly linked to the
IP of the service.  The Tor Hidden Service also provides protection of
the location of the service.

A current weakness of this system is that the service is considered a
trusted third party.  If the service is compromised, the documents can
be extracted and the author revealed.  We considered other
architectures, for example, one that delivered a more feature full
application to the browser, however this would be more like a content
delivery system.

Additionally, by multi-author implementation exposes the target
document to another user.  Therefore, the circle of trust is extended
from the service to the other party.  There is also no authentication
of the other party.  The service should provide an OTR like mechanism
for inviting the other party into the editing session and verifying
the authenticity of the user.

\section{Implementation Details}\label{sec:impl}

We implemented a web application based on the Play Web Application
Framework in Java. This web application had a reference to a modified
version of JSAN which was forked from the PSAL Anonymouth repository
\cite{PSAL:github}. In addition the application has major dependencies
on JQuery, Twitter Bootstrap (for page layout), and Etherpad (an
open-source collaborative text editing web application and library)
\cite{etherpad}. Etherpad (specifically Etherpad Lite is the version
used here) in turn has major dependencies on node.js for building and
running the backend service.  Figure \ref{fig:text_endpoint} shows an
example screenshot of the stylometric only endpoint.

\begin{figure}
  \centering
    \includegraphics[width=0.4\textwidth]{img/text_endpoint.png}
  \caption{Screenshot of the text endpoint}
  \label{fig:text_endpoint}
\end{figure}

At a high level the implementation is as follows: A user browses to
the Stylometry Service via a web browser. This causes the Play
Framework web application to serve up a web page with an Etherpad
control and instructions for the user to enter in the document they
wish to anonymize. The Etherpad control is implemented as an iframe
which serves an Etherpad that is connected to the node.js server
running the Etherpad backend (both servers should reside on the same
domain, running on different ports). The page served by Play also
contains a button which allows the author to specify when he or she
would like to submit the document for anonymization to
Anonymouth. Because the Anonymouth analysis process depends on a
number of computationally-intensive algorithms (among them running SMO
analysis in Weka as well as a Basic-9 feature stylometric analysis) we
implemented this calculation asynchronously. When a user clicks the
button to run an analysis, JQuery is used to issue a HTTP POST
containing in the message body a JSON-encoded representation of the
current Etherpad text to an endpoint at
\url{/getAnonymouthInfoJSON}. During the time that the Anonymouth
analysis is underway, a spinner control from the spin.js library is
used to indicate to the user than an analysis is underway. The fact
that the request is made to Anonymouth asynchronously allows a user to
continue editing the text while an analysis is running, allowing for a
smooth user experience.

Figure \ref{fig:impl} shows the current implemented service in a
layered architecture.  There are currently two endpoints that run in
the Play Framework: a pure stylometric endpoint and the adversarial
endpoint.  The adversarial endpoint is Anonymouth and also contains
Etherpad, the collaborative editor.  Currently, the endpoints are both
meant to run on the same server.

\begin{figure}
  \centering
    \includegraphics[width=0.2\textwidth]{img/impl.pdf}
  \caption{Current implementation of JSANaaS as a layered drawing}
  \label{fig:impl}
\end{figure}

The web service as implemented currently supports only one author as the
assumption is made that the author has pre-configured the document set
(also referred to as \emph{problem set} in Anonymouth source code) that provides
references as to the author's own writing style, as well as writing
samples for other authors that will be used as a reference for writing
styles that are different than that of the active author. The user can
additionally configure the Anonymouth properties file
(\texttt{anonymouthprop.prop}) in the JSAN resources directory to influence
settings such as the feature set to use for stylometric identification
as well as the number of threads to use and maximum number of features
to analyze.

One configured, the call to the \texttt{getAnonymouthInfoJSON} input
will overwrite the \texttt{test.txt} file on disk that is configured
in the provided problem set. This will ensure that changing the
document in Etherpad forces an update to the test file and thus
ensuring that the 'latest' document is always anonymized. Once the
problem set has been updated, the Anonymouth library is invoked. The
Anonymouth library is a forked version of the current Anonymouth
application, which is designed to be used behind a Swing/AWT rich
client GUI. A number of implementation challenges were present when
trying to separate the core anonymization logic of Anonymouth from its
GUI implementation - most specifically, although an engine namespace
exists which holds much of the anonymization logic, significant
dependencies still existed between the engine and the GUI
namespaces, specifically in the event handlers associated with the
Editor screen and the \texttt{GUIMain} classes. Much of the work in
this project consisted of reducing the coupling between these two
namespaces.

As much of the configuration logic was handled at the GUI layer (via
\texttt{ThePresident} and \texttt{GUIMain} classes) we took the
approach of refactoring the GUI layer to work in a 'headless' mode,
that is, without any windows launching. Long-term it would be
preferable to have no dependencies on the GUI namespace at all for the
Stylometry Service, however this could not be achieved in the
available time frame for this project. The web service thus invokes a
modified version of the \texttt{ThePresident} class, which coordinates
reading configuration files, loading the configured problem set, and
using numerous libraries (JGAAP and Weka among them) to conduct an
adversarial stylometric analysis. The results are returned by the web
service in the form of a JSON-encoded list of words to remove, as well
as an indication of 'changes needed' to the current text to reach an
acceptable level of anonymity.

@@

\subsection{Deployment}

@@

\subsection{Comparison to Stand-alone Application}

The stand-alone application has both advantages and disadvantages
relative to the web service. To start with advantages: it contains
more robust error handling, offers a GUI to create a problem set, and
provides a richer editing experience for anonymized
texts. Disadvantages concern ease of use (users must download and
execute a JAR file) and supported platforms (it is unlikely that this
JAR file will be supported on many mobile phones, for instance). The
Stylometry Service, shown in Figure \ref{fig:text_endpoint}, in
contrast, is potentially more accessible than the standalone
application: it can be accessed via mobile phones and tablets, for
instance. Likewise application delivery may be simpler - nothing must
be downloaded locally. Furthermore, the web application maintains a
time line of changes made to a text and also allows for simple
multi-party anonymization of documents.

Disadvantages to the web application include the fact that it offers
fewer anonymization features (for instance, highlighting of specific
text passages), instead focusing primarily on ``words to
remove''. Furthermore, its security footprint is less well known, as it
introduces a number of new dependencies / potential attack vectors
such as JQuery, Twitter Bootstrap, Etherpad Lite, node.js, etc.

\section{Evaluation}\label{sec:evaluation}

We conducted two evaluations of the service.  The first was a
single-user evaluation that focused on the stylometric capabilities.
The second was a multi-user evaluation.  In this evaluation, the focus
was on the experience and usability of a multi-user stylometric
interaction.

\subsection{Single User Evaluation}

@@

\subsection{Multiple Concurrent User Evaluation}

A simple multi-user evaluation was conducted.  The noticeable feature
in the multi-user scenario was the real-time collaboration.  An example
screen shot in Figure \ref{fig:multi}.  When an experienced user
interacted with a novice user, the learning curve of the novice user
was drastically reduced.  The multi-user platform also allows users to
divide and conquer the work, which allowed for quicker anonymization
of the document.

\begin{figure}
  \centering
    \includegraphics[width=0.5\textwidth]{img/mult_user.png}
  \caption{Multi-user screenshot}
  \label{fig:multi}
\end{figure}

In this multi-user test, both authors were human.  However, we would
like to see the multi-user as an Artificial Intelligence (AI) Agent.
The agent, acting as a author, could help the primary author anonymize
the target document.  We believe that this application is well-suited
for an AI because of a clear objective function: the changes-needed
score.  A naive approach could simply apply adversarial search with
pruning, like Mini-max to analyze the document and replace each
suggested word with a thesaurus lookup.

A more thorough approach is to incorporate a Drama Manager agent as
found in video games \cite{10.1109/WI-IAT.2009.143},
\cite{conf/aaaiss/SullivanCM09}, \cite{Magerko04aicharacters}.  In
these games, a Drama Manager (DM) acts as a benevolent AI to manage the
player's experience.  The DM monitors various features of the game and
can change elements in game.  If the game is too challenging, the DM
can scale the difficulty by offering additional power-ups, or if it is
too easy, the DM will introduce more adversaries.

The application to this service is that the AI can monitor the user's
interaction on the site.  If the user is slow to start using the
software, the agent can offer helpful tips.  However, an experienced
user will immediately start using the service and would not need these
tips.  Similarly, if the user is not replacing words in a direction
that improves the document, the agent, acting as a second author, can
offer assistance.

\subsection{Evaluation of Architecture Qualities}

In the following sections, we analyze each architecture against the
design criteria in Section \ref{sec:design}.  We evaluate our
implementation as of the time of this writing and identify areas that
need further work.

As implemented the service runs on one host and none of the redundancy
or resiliency features have been added.  This may be acceptable for a
prototype, but for the service to act as a research platform, more
work must be done to ensure that it is reliable.  We did not perform
any hardening or enhance the protection of the web service through the
operating system in any way.  Each of those efforts would certainly
help maintain the availability goal.

\subsubsection{Interoperability}

We have tested the current software with popular web browsers and each
of them have been able to interact with the site.  The heavy lifting
of this interoperability is the Play Framework, which allows for rapid
development of a RESTful web service.  Even though the client software
need only a browser, there is great variety in browsers.  Again,
restricting the browser to the Tor Browser Bundle would significantly
help otherwise various browsers could have unique interoperability issues.

\subsubsection{Modifiability}

We did not implement the registration service, therefore the service
is not as modifiable as we would like.  The main purpose of this
effort was to evaluate the feasibility and during the development we
could rapidly push changes to the server.  The Play Framework assists
greatly in this effort, but inherently, web service development can
lead to quicker deployments than traditional applications.

The performance of the Stylometry Service as implemented is largely
determined by that of the Anonymouth service that it uses to get
stylometry suggestions. For an analysis of 1 500-word test document vs
23 documents from 4 'other' authors and using 8 training documents
from the to-anonymize author, we recorded a total of 67 seconds
required for the Anonymouth analysis, with less than 1 additional
second used to update the client UI, on a 3.3 GHz Core i5 Ubuntu 12.04
Desktop machine, using 1 calculation thread for Anonymouth. These
results suggests that any attempts at performance optimization should
center around optimizing the performance of the Anonymouth
configuration.

After each stylometric analysis is complete, the web service ensures
all relevant Anonymouth resources are closed. This allows the web
service to be used over a long period of time (20 or more
anonymization attempts have been tested) without memory leaks noted.

@@

@@

\subsubsection{Security and Privacy}

Security and Privacy findings were analyzed in Sections
\ref{sec:security} and \ref{sec:privacy}.

\subsubsection{Usability}

We feel that the interaction with the interface is improved as web
service.  The web service provides a very common experience for the
user through her browser with limited options.  The software is a
prototype and overall, the interface is intuitive and similar to other
web applications.  The addition of the Etherpad enables a very easy
collaborative editing platform and the suggested words and very
clearly identified.

@@

There are two significant contributions as a result of this work.  The
first is a stylometric web service.  This advances the usability
and capabilities of JSAN and provide a framework for more expansive
user testing in the future. The user testing results suggest that a
web interface may offer usability advantages while still providing a
meaningful increase in author anonymity.

The second contribution is that this is the first framework for
multi-author adversarial stylometry.  Our results here suggest
multi-author collaboration and improve the usability of the software
through real-time mentoring.  Also, the addition of an AI agent could
replace the human mentor and provide a more consistent experience.

While the software is a prototype, we believe that a stylometric web
service is feasible.  There are challenges to overcome, such as the
trusted service provider, but we feel that these are solvable.

@@

@@

With a web service, we can offer real-time adversarial stylometry.
Assume Alice, who has a blog, wants to anonymize her next blog post.
She would connect to our web service, submit the URL for her blog and
then write her next post with adversarial stylometry.  This real-time
data crawling at this scale is simply not feasible with stand alone
software.  Currently the corpus must be selected before deployment of
the service, but building a corpus on the fly would be interesting.
However, there are challenges since the  data is especially raw.
For example, the author may have signed her name to the blog post or
left in other details that could threaten her anonymity.

A third party could re-write the document entirely.  In this case, it
is important to obfuscate the content from the re-writer.  One idea,
is to mix the document, perhaps with other documents, prior to
re-writing.  The re-writer would be presented with an otherwise
nonsensical document and would focus on re-write each sentence in her
native style.  The combined document, would contain $n$ author styles,
where $n$ is the number of re-writing authors.  The concern lies with
storing the document and making it available to re-writers.  We
eliminated this complication by focusing on real-time anonymization in
a low-latency environment.  The third party re-writer could also be
achieved by an AI agent, which could eliminate this issue.
